DRAFT

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
```{r include=FALSE}
df <- read.csv('https://osf.io/yzntm/download')
```
```{r}
kable(funModeling::df_status(df))
```

## 1.2 Dataset for 7 Central European countries
### • For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))

@@

>>>>

```{r include=FALSE}
df <- read.csv('https://osf.io/yzntm/download')
```
## 1.2 Dataset for 7 Central European countries
### • For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))

@@

### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
```{r}
kable(funModeling::df_status(df))
```
